This is the title : v\versionnumber

### 2017-11-26 templates/livecoms-template-computationalcomparisons.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,lessons]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Please note that these options may affect formatting.

@@

\begin{abstract}
This particular document provides a skeleton illustrating key sections for a Lessons Learned document.
Please see the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates} for additional information on and examples of using the LiveCoMS LaTeX class.
Here we also assume familiarity with LaTeX and knowledge of how to include figures, tables, etc.; if you want examples, see the sample just referenced.

@@

Here you would explain what problem you are tackling and briefly motivate your work.
Since a Lessons Learned document provides negative results in a particular category, you will want to clearly define your category and also motivate the application of your work to your particular problem.

We suggest that you envision your document potentially extending in the future to include other Lessons Learned in the same category, so you may want to organize your work in a way which would allow this type of extension (e.g. providing a general introduction then using subsections to explain your particular problem) -- for example, describing potential of mean force calculations generally, then in a subsection motivating your particular application of them.

In this particular template, we have removed most of the usage examples which occur in \texttt{sample-document.tex} to provide a minimal template you can modify; however, we retain a couple of examples illustrating more unusual features of our templates/article class, such as the checklists, and information on algorithms and pseudocode.

A Lessons Learned document is a regular scientific article, and should be prepared with similar organization.
Sample typical section headers follow.

\section{Theory and Methods}

You should use a section (or separate sections, if this yields better organization) to describe the theory and methods relevant to your work.

This should include all information required for a reader to reproduce the results, including software version numbers and links to any in-house files or scripts

@@

You would give your results here.
Since the goal here is not just to present negative results, but also to provide lessons learned from doing so, you will want to make sure you have data to show why your approach failed.

\section{Discussion}

Discussion should highlight the lessons learned and give tips for avoiding future mistakes.
Try to tell readers what you wish you had known before starting.

\section{Conclusions}

Give conclusions.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,comparison]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Please note that these options may affect formatting.

@@

\begin{abstract}
This particular document provides a skeleton illustrating key sections for a Computational Comparisons document.
Please see the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates} for additional information on and examples of using the LiveCoMS LaTeX class.
Here we also assume familiarity with LaTeX and knowledge of how to include figures, tables, etc.; if you want examples, see the sample just referenced.

@@

Here you would explain what problem you are tackling and briefly motivate your work; why is a comparison needed here?
What do the tools you are comparing do?

In this particular template, we have removed most of the usage examples which occur in \texttt{sample-document.tex} to provide a minimal template you can modify but we retain an example on algorithms and pseudocode.

\section{Methodology}

Here (and in other sections if needed) you would describe how you compared the software in question, with subsections as needed.
Perhaps you may also need to comment here on why you did not include certain pieces of software or how these might be included in the future.

\subsection{Physical systems and properties}

What did you calculate, on what systems? Why did you make that choice?

\subsection{Methodology for comparison}
How did you compute what you're comparing? 
What software versions did you use?
How would the software be accessed?

\subsubsection{Method selection}
How did you select which protocols to use? How are you certain these are representative? Would a naive user get similar performance?

\subsubsection{Supporting files}
Are there run scripts or files others would need to reproduce your work? Are these provided in your GitHub repo, or how would they be accessed? 
How exactly would someone reproduce/extend this work?

\subsubsection{Error analysis}
You may wish to devote particular attention to error analysis.

@@

You would give results.

\section{Discussion and conclusions}

You may perhaps wish to revisit the issue of what performance a naive user might expect, here.
